Binocular integration of chromatic and luminance signals

### 2024-04-01 manuscript.qmd
Changing python path again

if (processdata>0){
  use_python('/lib/python3')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

>>>>

if (processdata>0){
  use_python('/usr/bin/python3')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}
